### 2009-07-30 SC09/arch.tex
attached is the most recent version of the paper.  I'll do another big push tomorrow and then I'll submit it since I'll be on vacation all next week.  I think I've addressed most of the reviewer's comments but here's a couple that maybe still need to be addressed (or ignored):
the addition of metadata benchmark such as mdtest would make paper
stronger

the paper does not mention about file locks.  file system semantics is
not clear.

there should be a discussion about file system approach vs library
approach.  library can speed up N-1 w/out sacrificing performance for
other ops like metadata q

\plfs\ is a virtual file system situated between the parallel application and
an \upfs\ responsible for the actual data storage. As \plfs\ is a virtual file
system, it leverages many of the services provided by the \upfs\ such as
redundancy, high availability, and a globally distributed data store.  This
frees \plfs\ to focus on just one specialized task: rearranging application
data so the N-1 write pattern is better suited for the \upfs.  In the remainder
of this paper,  we refer to \plfs\ generally to mean this virtual file system
which itself is comprised of a set of \plfs\ servers running across a compute
system bound together by an \upfs; when we refer to a {\em specific} \plfs\ we
mean just one of these servers.

@@

\subsubsection{Reading from \plfs}
\label{arch-read}
Rearranging data in this manner should improve write bandwidths, but
it also introduces additional complexity for reads. In order to read 
the logical file, \plfs\ maintains an \Term{index file} for each compute
node which records the logical offset and length of each write. \plfs\ can
then construct a \Term{global index} by aggregating the multiple index files 
into an offset lookup table.

>>>>

\plfs\ is a virtual FUSE file system, mounted on the compute nodes, situated between the parallel application and
an \upfs\ responsible for the actual data storage. 
As \plfs\ is a virtual file
system, it leverages many of the services provided by the \upfs\ such as
redundancy, high availability, and a globally distributed data store.  This
frees \plfs\ to focus on just one specialized task: rearranging application
data so the N-1 write pattern is better suited for the \upfs.  In the remainder
of this paper,  we refer to \plfs\ generally to mean this virtual file system
which itself is comprised of a set of \plfs\ servers running across a compute
system bound together by an \upfs; when we refer to a {\em specific} \plfs\ we
mean just one of these servers.

@@

\subsubsection{Reading from \plfs}
\label{arch-read}
Rearranging data in this manner should improve write bandwidths, but
it also introduces additional complexity for reads. In order to read 
the logical file, \plfs\ maintains an \Term{index file} for each compute
node which records the logical offset and length of each write. \plfs\ can
then construct a \Term{global index} by aggregating the multiple index files 
into an offset lookup table.  This global offset is constructed as needed to
satisfy read operations and lookup operations when cached metadata is not
available (as will be discussed in Section~\ref{arch-meta}).
